%!TEX program = xelatex
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-new}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Yurui}{Zhou}{ \urlstyle{same}
\href{mailto:me@yuruiz.com}{me@yuruiz.com} | 412-352-6225 | \href{http://www.linkedin.com/in/yuruiz} {lnked.in/yuruiz}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}

\runsubsection{Carnegie Mellon Univ}
\descript{| MS in Electrical Computer Engineering}
\location{Pittsburgh, PA | Dec 2014 \textbullet{} Cum. GPA: 3.43 / 4.0}
\sectionsep

\runsubsection{Tsinghua Univ}
\descript{| BS in Mechanical Engineering}
\location{Beijing, China | July 2013 \textbullet{} Cum. GPA: 87.45 / 100}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Objective
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Objective}
\content{I'd rather play a crucial and flexible role in a small, agile and stressful team than work as replaceable gear in a established giant one. I don't want to repeat myself day by day and am looking for opportunities that expose me to interdisciplinary challenges. I love building stuff from scratch, solving problems all the way t\itemindent-.5cmhrough and growing up with the product.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\subsubsection{Software Engineer | Microsoft Band}
\location{Oct 2015 – Now | Redmond, WA}
\begin{tightemize}
\item Microsoft Health Platform: Design and implemented the Android side feature to provide a better user experience  across Microsoft Band, Microsoft Health Cloud and Microsoft Health Android App. 
\item Microsoft Band Firmware: Design and implemented new Microsoft Band feature to improve user experience and boost market performance
\end{tightemize}

\sectionsep
\subsubsection{Software Engineer | Microsoft, OSG, WINCXE, Siplat}
\location{April 2015 – Oct 2015 | Redmond, WA}
\begin{tightemize}
\item Servicing bluetooth driver stack for Windows 8.1 and Windows 10.
\item Designed and Implemented a Bluetooth Device Simulator so that a virtualized bluetooth devices can be used to quickly validate Bluetooth Drivers.
\end{tightemize}
\sectionsep

\subsubsection{Research Assistant | Carnegie Mellon University, ECE}
\location{Feb 2014 – August 2014 | Pittsburgh, PA}
\content{Prototype a postural monitoring device that will empower seniors and their healthcare providers to prevent falls and avoid traumatic injuries.}
\begin{tightemize}
\item Designed the device circuit board to integrate micro controller, wireless bluetooth and inertial sensors.
\item Assembled and functional tested (lab and field) of the wearable inertial measurement system.
\item On board Programming on micro controller for realtime data collection.
\end{tightemize}
\sectionsep

\subsubsection{Engineer | Tsinghua University, DPIM}
\location{Jan 2013 – Dec 2013 | Beijing, China}
\content{Build up a robust sensor network inside mine tunnel for real time management and to assist rescue operation in case of emergency.}
\begin{tightemize}
\item Designed the device circuit board to integrate micro controller with high power antenna.
\item On board programming for dynamic network construction and management.
\item Implemented the localization algorithm for realtime sensor localization.
\end{tightemize}
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\section{Projects}
%
%\runsubsection{Bitcoin Smart Property}
%\descript{Head Graduate Research}
%\location{Jan 2014 – May 2014 | Pittsburgh, PA}
%\content{A solution to minimize trust needed in secured loans and property managing using a peer-to-peer bitcoin contract.}
%\begin{tightemize}
%\item Designed the transaction process and protocol.
%\item Designed the distributed contract program based on bitcoin network protocol.
%\item Implemented the distributed contract program and published the contract blocks to bitcoin network
%\end{tightemize}
%\sectionsep

%\runsubsection{Campus Wide Express delivery Lockers}
%\descript{Head Undergraduate Research}
%\location{Jan 2012 – Apr 2013 | Beijing, China}
%\content{This project was a campus-wide solution to the problem of express delivery that provided express delivery lockers throughout the campus.}
%\begin{tightemize}
%\item Designed the lockers architecture to enable remote control and monitor.
%\item Designed and implemented the locker functional process
%\item Developed the locker program to enable customer Identity Recognition.
%\end{tightemize}

%\sectionsep



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Skills}
\begin{minipage}[t]{.6\textwidth}
\subsection{Programming}
\descript{Over 10000 lines:}
C \textbullet{} Python \textbullet{} Java \\
\descript{Over 5000 lines:}
C++ \textbullet{} C\#\\
\sectionsep

\end{minipage}
\hfill
\begin{minipage}[t]{.35\textwidth}

\subsection{Software}
\descript{Proficient:}
Cadence \textbullet{} ProE \textbullet{} \LaTeX  \\
\descript{Familiar:}
Matlab \textbullet{} AutoCAD
\sectionsep

\end{minipage}
\end{document}  \documentclass[]{article}
